PhD Title \\ PhD Thesis

### 2024-06-10 Latex_files/Thesis/chapters/chapter 2/main.tex
updates

We can if we want further restrict the incident beam by applying setting the truncation angle to match our microscope object, this essentially applies a cut off point to the In order to compute the scattering from the target particle \textit{ott} uses the t-matrix method, this is not essential for a simple sphere but is essential for complex shaped particles such as dimers. The scattered and incident fields are then combined

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{fixed_polarisation.png}
\end{figure}

>>>>

We can if we want further restrict the incident beam by applying setting the truncation angle to match our microscope object, this essentially applies a cut off point to the In order to compute the scattering from the target particle \textit{ott} uses the t-matrix method, this is not essential for a simple sphere but is essential for complex shaped particles such as dimers. The scattered and incident fields are then combined together in the far field to get $I(x,y)$, the quadrant and overall signals are calculated via:
\begin{align}
	Q_i &= \sum_{n,m} I(x_{i,n}, y_{i,m}) \\
	S_{x} &= \frac{(Q_1+Q_2)-(Q_3+Q_4)}{\sum I_0(x,y)} \\
	S_{y} &= \frac{(Q_1+Q_3)-(Q_2+Q_4)}{\sum I_0(x,y)} \\
	S_{z} &= \frac{(Q_1+Q_2+Q_3+Q_4}{\sum I_0(x,y)}
\end{align}
Where the denominator is the total intensity on the QPD while there is no particle within the trap. The QPD sensitivity is dependent on both the polarisation of the incident beam and the displacement of the target sphere, this is shown in fig.~\ref{fig:totalfield}.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\linewidth]{fixed_polarisation.png}
	\captionsetup{margin=0.5cm}
	\caption{Total Field incident on the quadrant photo diode for a several different displacements. Top Left: $2\mu m $ diameter silica sphere placed at the focus of a  beam. Top Right: silica sphere is now displaced by $1 \mu m$ along the x-axis. Bottom Right: silica sphere is now displaced by $1 \mu m$ along the y-axis. Bottom Left: silica sphere is now displaced by $0.707 \mu m$ along the x and y axis. The trapping beam is a $TEM_00$ Gaussian, polarised along the along the x-axis. $S_x$, $S_y$, and $S_z$ are shown to the right of each graph, $Q_1$, $Q_2$, $Q_3$, and $Q_4$ are shown above each graph.}
	\label{fig:totalfield}
\end{figure}

Rather than displacing and rotating the particle itself, we instead rotate and displace the incident beam and recalculate the beam coefficients; the total beam is then inversely rotated in order to record the QPD signal. With this any trajectory can be collected from the QPD by displacing and rotating the beam accordingly, later in chapters \ref{chapter:langevin_dynamics} and \ref{chapter:simulated_detection} we discuss how to extract information from the QPD's outputted signal.

### 2024-06-10 Latex_files/Thesis/chapters/chapter 4/main.tex
updates

\chapter{Complex Langevin dynamics of spherical dimers}
Much of the calibration theory discussed in Chapter 2 assumes that the target particle in question is a single sphere, one who's scattering and motion is easily computed. However, while working with dense colloidal suspensions, one often ends up trapping more than one sphere. Li and Arlt \cite{Li2008} studied the case of two microspheres trapped in a single OT and found that multiple trapped beads could be mistaken for a single trapped bead with altered trap stiffness. Theoretical studies on the case of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a ray-optics based model to show that the two trapped beads are brought into physical contact with each other by optical forces and they also calculated the axial equilibrium positions of the two trapped beads as a function of their size. Experiments in \cite{Praveen2016} confirmed that the two trapped beads indeed experience different trap stiffnesses in the vicinity of the same potential well. There are further discussions looking into the dynamics of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, Chetana2022}, their results all showing that predicting the behaviour an arbitrary shaped particle comes with great difficulty due to the fact that the optical force is dependent on a greater number of variables such as orientation and size factors.

>>>>

\chapter{Complex Langevin dynamics of spherical dimers}
\label{chapter:langevin_dynamics}
Much of the calibration theory discussed in Chapter 2 assumes that the target particle in question is a single sphere, one who's scattering and motion is easily computed. However, while working with dense colloidal suspensions, one often ends up trapping more than one sphere. Li and Arlt \cite{Li2008} studied the case of two microspheres trapped in a single OT and found that multiple trapped beads could be mistaken for a single trapped bead with altered trap stiffness. Theoretical studies on the case of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a ray-optics based model to show that the two trapped beads are brought into physical contact with each other by optical forces and they also calculated the axial equilibrium positions of the two trapped beads as a function of their size. Experiments in \cite{Praveen2016} confirmed that the two trapped beads indeed experience different trap stiffnesses in the vicinity of the same potential well. There are further discussions looking into the dynamics of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, Chetana2022}, their results all showing that predicting the behaviour an arbitrary shaped particle comes with great difficulty due to the fact that the optical force is dependent on a greater number of variables such as orientation and size factors.
